Finite element analysis of multi-dimensional and simplified models for beams and plates

### 2024-04-10 final_seminar/main.tex
seminar

\documentclass[8pt]{beamer}
\usetheme{metropolis} % Use the Metropolis theme
\usepackage{pgfplots}

\usepackage[style=authoryear,backend=biber]{biblatex}
\addbibresource{../references.bib}

@@

\section{Theory}
    \subsection{General vibration problem}
        \begin{frame}{General vibration problem}
        \end{frame}

    \subsection{Existence and uniqueness of solutions}
        \begin{frame}{Existence and uniqueness of solutions}
        \end{frame}

    \subsection{Modal Analysis}
        \begin{frame}{Modal Analysis}
            General vibration problem:

@@

            *******************CHECK THIS*******************
            Existence of a solution is presented in the article [\cite{CVV18}]\footfullcite{CVV18}

@@

        \begin{frame}{Modal Analysis}
            Let $V$, $W$ and $X$ be real Hilbert spaces such that $W$ is a linear subspace of $X$, and $V$ is a linear subspace of $W$, i.e. $V \subset W \subset X$.
            \begin{itemize}
                \item[] X is the global space with inner product $(\cdot,\cdot)_X$ and the induced norm $||\cdot||_X$.
                \item[] W is the inertia space with inner product $(\cdot,\cdot)_W$ and the induced norm $||\cdot||_W$.
                \item[] V is the energy space with inner product $(\cdot,\cdot)_V$ and the induced norm $||\cdot||_V$.
            \end{itemize}
        \end{frame}

@@

\section{Numerical Results}
    \subsection{Finite Element Analysis}
        \begin{frame}{FEM}
        \end{frame}

@@

        \begin{frame}{Eigenvalue problem - Two and Three-dimensional models}
            General eigenvalue problem for the two- and three-dimensional models:

    \subsection{Validity of the Timoshenko beam model}
        \begin{frame}{Validity of the Timoshenko beam model}
        \end{frame}

    \subsection{Validity of the two-dimensional beam model}
        \begin{frame}{Validity of the two-dimensional beam model}
        \end{frame}

        \begin{frame}{Eigenvalue problem - FEM}
            \centering
            \includegraphics[scale=0.45]{Convergence.png} \\ % Adjust scale as needed
            \footnotesize Rate of convergence of the first 20 eigenvalues.
            \label{fig:conv}
        \end{frame}

@@

        \begin{frame}{Comparison of two and three-dimensional models}
            \centering
            \footnotesize
            \renewcommand{\arraystretch}{0.8}
            Results from [LVV09] and results obtained. $0^a$ indicates a 0 due to rounding. $\alpha = 1200$

@@

>>>>

\documentclass[8pt]{beamer}
\usetheme{metropolis} % Use the Metropolis theme
\usepackage{pgfplots}
\usepackage{caption,subcaption}
\usepackage[style=authoryear,backend=biber]{biblatex}
\addbibresource{../references.bib}

@@

\section{Theory}
    \subsection{General vibration problem}
        \begin{frame}{General vibration problem}
            \textbf{General vibration problem:}

            Find a function $u \in C(J,\ X)$ such that $u'$ is continuous at $0$ with respect to $\Vert \cdot \Vert_{W}$, and for each $t \in J$, $u(t) \in V$, $u'(t) \in V$, $u''(t) \in W$, satisfying
            \begin{eqnarray}
                c(u''(t),v)+a(u'(t),v)+b(u(t),v) = (f(t),v) \ \ \ \ \textrm{for each} \ v \in V, \label{eq:existence:ProblemGVarHom}
            \end{eqnarray}
            with initial conditions $u(0) = u_0$ and $u'(0) = u_1$.
        \end{frame}

    \subsection{Existence and uniqueness of solutions}
        \begin{frame}{Existence and uniqueness of solutions}
            Let $V$, $W$ and $X$ be real Hilbert spaces such that $W$ is a linear subspace of $X$, and $V$ is a linear subspace of $W$, i.e. $V \subset W \subset X$.
            \begin{itemize}
                \item[] X is the global space with inner product $(\cdot,\cdot)_X$ and the induced norm $||\cdot||_X$.
                \item[] W is the inertia space with inner product $(\cdot,\cdot)_W$ and the induced norm $||\cdot||_W$.
                \item[] V is the energy space with inner product $(\cdot,\cdot)_V$ and the induced norm $||\cdot||_V$.
            \end{itemize}
        \end{frame}

        \begin{frame}{Existence and uniqueness of solutions}
            The following assumptions are made in \cite{VV02} for the existence results.
            \begin{itemize}
                \item[] \textbf{A1} - $V$ is dense in $W$ and $W$ is dense in $X$.

                \item[] \textbf{A4} - The bilinear form $a$ is non-negative, symmetric and bounded on $V$, i.e. there exists a positive constant $K_a$ such that for $\displaystyle u,v \in V$, \[|a(u,v)| \leq K_a\Vert u \Vert_V \Vert v \Vert_V.\]
            \end{itemize}
        \end{frame}

        \begin{frame}{Existence and uniqueness of solutions}
            \newtheorem{Thmx}{Theorem}
            \begin{Thmx}
                Suppose assumptions \textbf{A1}-\textbf{A4} hold. If, for $u_0 \in V$ and $u_1 \in V$, there exists some $y \in W$ such that
                \begin{eqnarray}
                    b(u_0,v) + a(u_1,v) = c(y,v) \ \ \ \ \textrm{ for all } \ v \in V, \label{bilinear_equation}
                \end{eqnarray}
                then for each $f \in C^1(J,X)$, there exists a unique solution $u \in C^1(J,V)\cap C^2(J,W)$ for Problem GVar.
            \end{Thmx}

            This theorem allows for a solution of the abstract variational problem Problem GVar, if the assumptions \textbf{A1}-\textbf{A4} is satisfied and the initial values $u_0$ and $u_1$ are admissible. It is not always easy to verify that \eqref{bilinear_equation} is satisfied.
        \end{frame}

    \subsection{Modal Analysis}
        \begin{frame}{Modal Analysis}
            \textbf{General vibration problem:}

@@

            Existence of a solution is presented in the article [\cite{CVV18}]\footfullcite{CVV18}

@@

@@

\section{Numerical Results}
    \subsection{Finite Element Analysis}
        \begin{frame}{Eigenvalue problem - Two and Three-dimensional models}
            General eigenvalue problem for the two- and three-dimensional models:

@@

        \begin{frame}{FEM}
        \end{frame}

        \begin{frame}{Accuracy of the Eigenvalues}
            \centering
            \includegraphics[scale=0.3]{Convergence.png} \\ % Adjust scale as needed
            \footnotesize Rate of convergence of the first 20 eigenvalues.

            \centering
            \includegraphics[scale=0.3]{convergence3d.png} \\ % Adjust scale as needed
            \footnotesize Rate of convergence of the first 20 eigenvalues.
        \end{frame}

    \subsection{Validity of the Timoshenko beam model}
        \begin{frame}{Validity of the Timoshenko beam model}
            \begin{center}
                \begin{minipage}[b]{0.45\linewidth}
                    \centering
                    \begin{tikzpicture}[scale=0.7]
                        \draw[line width = 0.4mm] (0,0.2) -- (6,0.2);
                                    \draw[line width = 0.4mm] (0,-0.2) -- (6,-0.2);
                                    \draw[line width = 0.4mm] (6,-0.2) -- (6,0.2);

                                    \node at (6.2,0) {$h$};
                                    \node at (2.7,-0.45) {$\ell = 1$};

                                    \draw[line width = 0.1mm] (0,-1.5) -- (0,1.5);
                                    \draw[line width = 0.1mm] (0,1.5) -- (-0.2,1.4);
                                    \draw[line width = 0.1mm] (0,1.3) -- (-0.2,1.2);
                                    \draw[line width = 0.1mm] (0,1.1) -- (-0.2,1);
                                    \draw[line width = 0.1mm] (0,0.9) -- (-0.2,0.8);
                                    \draw[line width = 0.1mm] (0,0.7) -- (-0.2,0.6);
                                    \draw[line width = 0.1mm] (0,0.5) -- (-0.2,0.4);
                                    \draw[line width = 0.1mm] (0,0.3) -- (-0.2,0.2);
                                    \draw[line width = 0.1mm] (0,0.1) -- (-0.2,0);

                                    \draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.2);
                                    \draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.4);
                                    \draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.6);
                                    \draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.8);
                                    \draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1);
                                    \draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.2);
                                    \draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.4);
                                    \draw[line width = 0.1mm] (0,-1.5) -- (-0.2,-1.6);
                    \end{tikzpicture}
                    \captionof{figure}{Two-Dimensional Beam}
                \end{minipage}
                \hfill
                \begin{minipage}[b]{0.45\linewidth}
                    \centering
                    \begin{tikzpicture}[scale=0.7]
                        \draw[line width = 0.4mm] (0,0) -- (6,0);
                                \node at (2.7,-0.25) {$\ell = 1$};

                                \draw[line width = 0.1mm] (0,-1.5) -- (0,1.5);
                                \draw[line width = 0.1mm] (0,1.5) -- (-0.2,1.4);
                                \draw[line width = 0.1mm] (0,1.3) -- (-0.2,1.2);
                                \draw[line width = 0.1mm] (0,1.1) -- (-0.2,1);
                                \draw[line width = 0.1mm] (0,0.9) -- (-0.2,0.8);
                                \draw[line width = 0.1mm] (0,0.7) -- (-0.2,0.6);
                                \draw[line width = 0.1mm] (0,0.5) -- (-0.2,0.4);
                                \draw[line width = 0.1mm] (0,0.3) -- (-0.2,0.2);
                                \draw[line width = 0.1mm] (0,0.1) -- (-0.2,0);

                                \draw[line width = 0.1mm] (0,-0.1) -- (-0.2,-0.2);
                                \draw[line width = 0.1mm] (0,-0.3) -- (-0.2,-0.4);
                                \draw[line width = 0.1mm] (0,-0.5) -- (-0.2,-0.6);
                                \draw[line width = 0.1mm] (0,-0.7) -- (-0.2,-0.8);
                                \draw[line width = 0.1mm] (0,-0.9) -- (-0.2,-1);
                                \draw[line width = 0.1mm] (0,-1.1) -- (-0.2,-1.2);
                                \draw[line width = 0.1mm] (0,-1.3) -- (-0.2,-1.4);
                                \draw[line width = 0.1mm] (0,-1.5) -- (-0.2,-1.6);
                    \end{tikzpicture}
                    \captionof{figure}{Timoshenko Beam}
                \end{minipage}
            \end{center}
        \end{frame}

@@

        \begin{frame}{Comparison of two and three-dimensional models}
            \centering
            \footnotesize
            \renewcommand{\arraystretch}{0.9}
            Results from [LVV09] and results obtained. $0^a$ indicates a 0 due to rounding. $\alpha = 1200$

@@

    \subsection{Validity of the Two-dimensional beam model}
        \begin{frame}{Validity of the Two-dimensional beam model}
            \begin{center}
                \begin{minipage}[b]{0.45\linewidth}
                    \centering
                    \begin{tikzpicture}[scale=0.6]
                        \draw[line width = 0.3mm] (-0.1,1) -- (6.9,1);
                        \draw[line width = 0.3mm] (-0.1,-1) -- (6.9,-1);
                        \draw[line width = 0.3mm] (6.9,-1) -- (6.9,1);
                        \draw[line width = 0.3mm] (-0.1,-1) -- (-0.1,1);

                        \draw[line width = 0.3mm] (0.1,1.1) -- (7.1,1.1);
                        \draw[line width = 0.3mm] (7.1,-0.9) -- (7.1,1.1);

                        \draw[line width = 0.3mm] (-0.1,1) -- (0.1,1.1);
                        \draw[line width = 0.3mm] (6.9,1) -- (7.1,1.1);
                        \draw[line width = 0.3mm] (6.9,-1) -- (7.1,-0.9);

                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});

                        \draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
                        \draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
                        \draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});

                        \draw[scale=0.5, domain=0.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});
                        \draw[scale=0.5, domain=1.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
                        \draw[scale=0.5, domain=2.5:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});

                        \draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
                        \draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
                        \draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
                        \draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
                        \draw[scale=0.5, domain=-3:-0.1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
                        \draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
                        \draw[scale=0.5, domain=-3:1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
                        \draw[scale=0.5, domain=-3:2, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});

                        \node at (6.95,1.25) {$b$};
                        \node at (6.78,0) {$h$};
                        \node at (3.2,-1.2) {$\ell = 1$};
                    \end{tikzpicture}
                    \captionof{figure}{Three-Dimensional Beam}
                \end{minipage}
                \hfill
                \begin{minipage}[b]{0.45\linewidth}
                    \centering
                    \begin{tikzpicture}[scale=0.6]
                        \draw[line width = 0.3mm] (0,1) -- (7,1);
                        \draw[line width = 0.3mm] (0,-1) -- (7,-1);
                        \draw[line width = 0.3mm] (7,-1) -- (7,1);
                        \draw[line width = 0.3mm] (0,-1) -- (0,1);

                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+4});
                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3.5});
                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+3});
                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2.5});
                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+2});

                        \draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
                        \draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});

                        \draw[scale=0.5, domain=1:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1.5});
                        \draw[scale=0.5, domain=2:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+1});

                        \draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x+0.5});
                        \draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x});
                        \draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-0.5});
                        \draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1});
                        \draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-1.5});
                        \draw[scale=0.5, domain=-3:0, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2});
                        \draw[scale=0.5, domain=-3:1, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-2.5});
                        \draw[scale=0.5, domain=-3:2, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3});
                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-3.5});
                        \draw[scale=0.5, domain=-3:3, smooth, variable=\x,densely dotted] plot ({\x}, {0.5*\x-4});

                        \node at (7.2,0) {$h$};
                        \node at (3.2,-1.2) {$\ell = 1$};
                    \end{tikzpicture}
                    \captionof{figure}{Two-dimensional Beam}
                \end{minipage}
            \end{center}
        \end{frame}
